---
output: rmarkdown::github_document
---

# carbondater

Estimate the Age of Web Resources

## Description

Methods are provided to read 'URL' metadata and scan web archives/use
web archive 'APIs' to determine the approxate age of the resource.

## What's Inside The Tin

The following functions are implemented:

- `get_date_from_url`:	Locate and retrieve publication date from a URL
- `get_earliest_mementos`:	Retrieve the earliest mementos for a URL/URI
- `get_earliest_pubdate`:	Retrieve the earliest "pubdate" for a URL
- `get_last_modified`:	Retrieve the last-modified header

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/carbondater")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(carbondater)
library(tidyverse)

# current verison
packageVersion("carbondater")

```

### Mementos

```{r}
get_earliest_mementos("http://www.cs.odu.edu")
```

### Last Modified

```{r}
get_last_modified("http://example.org/")
```

```{r}
get_earliest_pubdate("http://www.cnn.com/2011/10/28/living/ways-to-look-better-is/index.html")
```

```{r}
get_date_from_url(
  "https://rud.is/b/2018/05/03/seventeen-minutes-from-tweet-to-package/"
)
```